QALY Comparison - Living Wage Intervention

### 2023-11-07 minos/testing/QALY_comparison_livingWage.Rmd
Removed the 1st and 100th percentiles from some outputs

@@

```{r}
base.auc <- base %>%
  group_by(run_id) %>%
  summarise(AUC = auc(x=year, y = QALYs, type = 'spline')) %>%
  mutate(intervention = 'baseline')

wage.auc <- wage %>%
  group_by(run_id) %>%
  summarise(AUC = auc(x=year, y = QALYs, type = 'spline')) %>%
  mutate(intervention = 'LivingWage')

combined.auc <- rbind(base.auc, wage.auc)
```

```{r}
print(combined.auc)

combined.auc.plot <- combined.auc %>%
  group_by(intervention) %>%
  summarise(sd = sd(AUC),
            se = sd / sqrt(n()),
            AUC = mean(AUC))

ggplot(data = combined.auc.plot, aes(x = intervention, y = AUC, group = intervention, fill = intervention)) +
  geom_col() +
  geom_errorbar(aes(ymin = AUC - se, ymax = AUC + se, width = 0.4, group = intervention)) +
  labs(title = 'Total AUC comparison', subtitle = 'Baseline vs Living Wage Intervention') +
  xlab('Intervention')
```

@@

```{r}
combined.cost <- combined %>%
  #select(-alive_pop, -SF_12_MCS, -SF_12_PCS, -utility) %>%
  select(run_id, year, alive_pop, total_boost, intervention, QALYs) %>%
  mutate(QALY_value = QALYs * 60000)

ggplot(combined.cost, aes(x = year, y = QALY_value, group = intervention, colour = intervention)) +
  geom_smooth() +
  scale_y_continuous(label = comma)

combined.cost.change <- combined.cost %>%
  select(run_id, year, intervention, QALY_value) %>%
  pivot_wider(names_from = 'intervention',
              values_from = 'QALY_value') %>%
  mutate(change_baseline = baseline - baseline,
         change_LivingWage = livingWageIntervention - baseline) %>%
  select(-baseline, -livingWageIntervention) %>%
  pivot_longer(cols = change_baseline:change_LivingWage,
               names_to = 'intervention',
               names_prefix = 'change_',
               values_to = 'QALY_value_change') %>%
  filter(intervention != 'baseline')

ggplot(combined.cost.change, aes(x = year, y = QALY_value_change, group = intervention, colour = intervention, fill = intervention)) +
  geom_smooth() +
  scale_y_continuous(label = comma)
```

```{r}
total.combined.cost <- combined.cost.change %>%
  group_by(run_id, intervention) %>%
  summarise(TotalChange = sum(QALY_value_change)) %>%
  group_by(intervention) %>%
  summarise(se = sd(TotalChange) / sqrt(n()),
            TotalChange = mean(TotalChange))

#print(paste0('Total combined cost == ', format(round(as.numeric(total.combined.cost), 1), nsmall=1, big.mark=",")))

ggplot(total.combined.cost, aes(x = intervention, y = TotalChange, group = intervention, fill = intervention)) +
  geom_col() +
  geom_errorbar(aes(ymin = TotalChange - se, ymax = TotalChange + se, width = 0.4, group = intervention)) +
  scale_y_continuous(label = comma) +
  labs(title = 'Total Change in QALY Value', subtitle = 'Baseline vs Living Wage Intervention') +
  xlab('Intervention')

ggplot(combined.cost.change, aes(x = QALY_value_change, group = intervention, colour = intervention, fill = intervention)) +
  geom_histogram() +
  facet_wrap(~year) +
  labs(title = 'QALY value change')
```

@@

```{r}
combined.cost.mean <- combined.cost %>%
  group_by(run_id, year, intervention) %>%
  summarise(across(everything(), mean))

# ICER = (C1 - C0) / (E1 - E0)
# where
# C1 = cost of intervention
# E1 = effect of intervention
# C0 = cost of control group
# E0 = effect of control group

ICER <- combined.cost.mean %>%
  select(run_id, year, intervention, total_boost, QALYs, QALY_value) %>%
  pivot_wider(names_from = 'intervention',
              values_from = c('total_boost', 'QALYs', 'QALY_value')) %>%
  mutate(ICER = (total_boost_livingWageIntervention - total_boost_baseline) / (QALYs_livingWageIntervention - QALYs_baseline)) %>%
  select(run_id, year, ICER) %>%
  mutate(intervention = 'LivingWage')

ggplot(ICER, aes(x = year, y = ICER)) +
  geom_smooth() +
  scale_y_continuous(label=comma)

ICER.final <- ICER %>%
  group_by(run_id, intervention) %>%
  summarise(ICER = mean(ICER)) %>%
  group_by(intervention) %>%
  summarise(se = sd(ICER) / sqrt(n()),
            ICER = mean(ICER))

ggplot(ICER.final, aes(x = intervention, y = ICER, group = intervention, fill = intervention)) +
  geom_col() +
  geom_errorbar(aes(ymin = ICER - se, ymax = ICER + se, width = 0.4, group = intervention)) +
  scale_y_continuous(label = comma) +
  labs(title = 'ICER', subtitle = 'Living Wage Intervention') +
  xlab('Intervention')

```{r}
ggplot(ICER, aes(x = ICER, group = intervention, colour = intervention, fill = intervention)) +
  geom_histogram() +
  facet_wrap(~year) +
  labs(title = 'ICER by run', subtitle = 'All Years')

ggplot(filter(ICER, year == 2022), aes(x = ICER, group = intervention, colour = intervention, fill = intervention)) +
  geom_histogram() +
  labs(title = 'ICER by run', subtitle = '2022')

ggplot(filter(ICER, year == 2028), aes(x = ICER, group = intervention, colour = intervention, fill = intervention)) +
  geom_histogram() +
  labs(title = 'ICER by run', subtitle = '2028')

ggplot(filter(ICER, year == 2031), aes(x = ICER, group = intervention, colour = intervention, fill = intervention)) +
  geom_histogram() +
  labs(title = 'ICER by run', subtitle = '2031')

ggplot(filter(ICER, year == 2034), aes(x = ICER, group = intervention, colour = intervention, fill = intervention)) +
  geom_histogram() +
  labs(title = 'ICER by run', subtitle = '2034')
```

>>>>

```{r}
diff <- combined %>%
  pivot_longer(cols = -c(run_id, year, intervention, total_pop_size, alive_pop, dead_pop),
               names_to = 'measure') %>%
  group_by(run_id, year, measure) %>%
  summarise(diff = value[intervention == 'livingWageIntervention'] - value[intervention == 'baseline']) %>%
  pivot_wider(names_from = 'measure',
              values_from = 'diff')

wage.short <- wage %>%
  select(run_id, year, total_pop_size, alive_pop, dead_pop)

combined.diff <- merge(wage.short, diff, by=c('run_id', 'year'))

qalys_3sd <- 3 * sd(combined.diff$QALYs)
combined.culled <- filter(combined.diff, 
                          QALYs < QALYs + qalys_3sd,
                          QALYs > QALYs - qalys_3sd)

  # pivot_wider(id_cols = c(run_id, year),
  #             names_from = 'intervention',
  #             values_from = -c(run_id, year)) %>%
  # mutate(across(ends_with('_livingWageIntervention'), .names = "{.col}_diff") - across(ends_with('_baseline')))
```

@@

@@

```{r}
cost.per.qaly(base = base,
              base.name = 'baseline',
              int = wage,
              int.name = 'livingWageIntervention',
              QALY_value = 60000)  # QALY value == £60,000
```

```{r}
# total.combined.cost <- combined.cost.change %>%
#   group_by(run_id, intervention) %>%
#   summarise(TotalChange = sum(QALY_value_change)) %>%
#   group_by(intervention) %>%
#   summarise(se = sd(TotalChange) / sqrt(n()),
#             TotalChange = mean(TotalChange))
# 
# #print(paste0('Total combined cost == ', format(round(as.numeric(total.combined.cost), 1), nsmall=1, big.mark=",")))
# 
# ggplot(total.combined.cost, aes(x = intervention, y = TotalChange, group = intervention, fill = intervention)) +
#   geom_col() +
#   geom_errorbar(aes(ymin = TotalChange - se, ymax = TotalChange + se, width = 0.4, group = intervention)) +
#   scale_y_continuous(label = comma) +
#   labs(title = 'Total Change in QALY Value', subtitle = 'Baseline vs Living Wage Intervention') +
#   xlab('Intervention')
# 
# ggplot(combined.cost.change, aes(x = QALY_value_change, group = intervention, colour = intervention, fill = intervention)) +
#   geom_histogram() +
#   facet_wrap(~year) +
#   labs(title = 'QALY value change')
```

@@

```{r}
ICER(base = base,
     base.name = 'baseline',
     int = wage,
     int.name = 'livingWageIntervention',
     QALY_value = 60000)
```

```{r}
# ggplot(ICER, aes(x = ICER, group = intervention, colour = intervention, fill = intervention)) +
#   geom_histogram() +
#   facet_wrap(~year) +
#   labs(title = 'ICER by run', subtitle = 'All Years')
# 
# ggplot(filter(ICER, year == 2022), aes(x = ICER, group = intervention, colour = intervention, fill = intervention)) +
#   geom_histogram() +
#   labs(title = 'ICER by run', subtitle = '2022')
# 
# ggplot(filter(ICER, year == 2028), aes(x = ICER, group = intervention, colour = intervention, fill = intervention)) +
#   geom_histogram() +
#   labs(title = 'ICER by run', subtitle = '2028')
# 
# ggplot(filter(ICER, year == 2031), aes(x = ICER, group = intervention, colour = intervention, fill = intervention)) +
#   geom_histogram() +
#   labs(title = 'ICER by run', subtitle = '2031')
# 
# ggplot(filter(ICER, year == 2034), aes(x = ICER, group = intervention, colour = intervention, fill = intervention)) +
#   geom_histogram() +
#   labs(title = 'ICER by run', subtitle = '2034')
```
